---
title: "CI Results Plot"
author: "Leanne Nagels"
date: "Generated on: `r date()`"
output: 
  html_document:
    toc: true
    code_folding: show
    toc_float: 
        collapsed: false
        smooth_scroll: true
    number_sections: false
---

# Description 
This R Markdown File can be used to plot results of CI children for the Fishy experiment from the PICKA Project.

# Load packages and data
Load the required packages and download the required files. 

```{r setup, message=F, echo=F, eval=T}
# some custom options to generate a nice html file
options(digits = 3)
options(width=100)
library(knitr)
opts_chunk$set(cache=F, comment='#', tidy = T, tidy.opts=list(blank=T, width.cutoff=100), fig.align='center', message=T, warning=T, fig.width=8, fig.height=8, dev='png',eval=T)

# test if the necessary packages are installed if not, install them
packages <- c("ggplot2", "RColorBrewer", "reshape2","Rmisc","lmerTest","lme4","optimx","vctrs", "moments","ez","DescTools","optimx","ggpubr","ggnewscale","Hmisc")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())), repos='http://cran.us.r-project.org')  
}

# Load required packages
library(ggplot2)
library(RColorBrewer)
library(reshape2)
library(Rmisc)
library(lmerTest)
library(lme4)
library(optimx)
library(moments)
library(ez)
library(DescTools)
library(optimx)
library(ggpubr)
library(ggnewscale)
library(Hmisc)

# Set PICKA WD for CI data
# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/PICKA Experiments/')

# Read CSV file Results Fishy
dat<-read.csv('./Experiments/fishy/results/jvo_db_results.csv',header=TRUE)


# Open demographics table with subject,age (yy;mm), group, gender, and vocabulary score
CIdem<-read.table('demographsCI.txt', header=TRUE)


cor.test(x=CIdem$age, 
         y=CIdem$ageimp, method="pearson")

cor.test(x=CIdem$age, 
         y=CIdem$expci, method="pearson")


cor.test(x=ci.dat$ageimp, 
         y=ci.dat$expci, method="pearson")




CIdem$age<-NULL
CIdem$group<-NULL
CIdem$gender<-NULL
CIdem$vocabulary<-NULL
CIdem$ageimp<-NULL

# Set PICKA WD for NH data
# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/PICKA Experiments_NH/')

# Open demographics table with subject,age (yy;mm), group, gender, and vocabulary score
dem<-read.table('demographs.txt', header=TRUE)


#CIdem$group<-revalue(CIdem$group, c("04-06"="4-6", "06-08"="6-8", "08-10"="8-10", "10-12"="10-12", "12-14"="12-14", "14-17"="14-17"))
dem$gender<-as.factor(dem$gender)

# Merge dataframes
dat<-merge.data.frame(dat,dem, by='subject')


# no UK partiCIpants in datastruct
dat <- dat[grepl('gb',dat$subject)!=1,]


# Exclude some partiCIpants
# hearing thresholds too high for normal-hearing criteria
dat <- dat[dat$subject!="nl_NHA001",]
# test run
dat <- dat[dat$subject!="nl_NHK100",]
# incorrect comprehension of the task, only female responses
dat <- dat[dat$subject!="nl_NHK008",]
# dyslexia
dat <- dat[dat$subject!="nl_NHK022",]
# only completed Fishy and unreliable responses, no attention
dat <- dat[dat$subject!="nl_NHK043",]
# autism 
dat <- dat[dat$subject!="nl_NHK050",]


# Rename dat$dir_voice 
dat$dir_voice <- ifelse(dat$dir_voice=="male-gpr","F0","VTL")
dat$dir_voice<-as.factor(dat$dir_voice)


#add variable to identify CI and NH groups
dat$CI<-"NA"
dat[grepl('CI',dat$subject)==1,]$CI<-"CI"
dat[grepl('NH',dat$subject)==1,]$CI<-"NH"


# Variable CI is a factor
dat$CI<-as.factor(dat$CI)
dat$CI<-relevel(dat$CI, ref="NH")
# Log-transformed thresholds
dat$thrs.a.log<-log(dat$threshold)
dat$thrs.g.log<-log(dat$threshold_geom)


#Add exp CI variable for CI children
dat$expci<-dat$age
subjects<-unique(CIdem$subject)
for (i in subjects){
dat[dat$subject==i,]$expci<-CIdem[CIdem$subject==i,]$expci
}

```


# Information data

```{r lookat}
head(dat)
str(dat)
#summary(dat)

```



# Figure 1: Fishy JNDs CI and NH shaded area
``` {r plot accuracy individual dots}


# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/Desktop/CI Paper/Figures')


dat$group<-factor(dat$group, levels=c("04-06","06-08","08-10","10-12","12-14", "14-17","adults"))



#add variable plot_age to have adult data in same plot
dat$plot_age<-dat$age
adults_num <- length(unique(dat$subject[dat$group=="adults"]))
dat[dat$group=="adults",]$plot_age <- c(18.1, 18.3, 18.5, 18.6, 18.7, 18.8, 18.9, 19, 19.1, 19.2, 19.3, 19.4, 19.5, 19.7, 19.9)

#make subsets of data frame
kid.dat<-dat[dat$group!="adults",]
#kid.dat$subject <- droplevels(kid.dat$subject)
nh.kid.dat<-kid.dat[kid.dat$CI=="NH",]


nh.dat<-dat[dat$CI=="NH",]
#nh.kid.dat$subject <- droplevels(nh.kid.dat$subject)
#nh.kid.dat$group <- droplevels(nh.kid.dat$group)

ci.dat<-dat[dat$CI=="CI",]
#CI.kid.dat$subject <- droplevels(CI.kid.dat$subject)
#CI.kid.dat$group <- droplevels(CI.kid.dat$group)


# Make predictions based on NH child data 
# Based on tutorial by https://aosmith.rbind.io/2018/11/16/plot-fitted-lines/
# and http://www.sthda.com/english/articles/40-regression-analysis/166-predict-in-r-model-predictions-and-confidence-intervals/#prediction-interval

# nh.kid.dat.f0<-nh.kid.dat[nh.kid.dat$dir_voice=="F0",]
# nh.kid.dat.vtl<-nh.kid.dat[nh.kid.dat$dir_voice=="VTL",]
# 
# 
# fitlm.f0 = lm(thrs.g.log ~ age, data = nh.kid.dat.f0)
# #nh.kid.dat.f0$predlm = predict(fitlm.f0)
# predslm.f0 = predict(fitlm.f0, interval = "predict", level=0.5)
# datlm.f0<-merge.data.frame(nh.kid.dat.f0,predslm.f0, by="row.names",all.x=TRUE)
# 
# 
# fitlm.vtl = lm(thrs.g.log ~ age, data = nh.kid.dat.vtl)
# #nh.kid.dat$predlm = predict(fitlm)
# predslm.vtl = predict(fitlm.vtl, interval = "predict", level=0.55)
# datlm.vtl<-merge.data.frame(nh.kid.dat.vtl,predslm.vtl, by="row.names",all.x=TRUE)
# 
# datlm = rbind(datlm.f0, datlm.vtl)



fitlm = lm(thrs.g.log ~ age, data = nh.kid.dat)
#nh.kid.dat$predlm = predict(fitlm)
predslm = predict(fitlm, interval = "predict", level=0.5)
datlm<-cbind(nh.kid.dat,predslm)

# For ASA poster, extra dot with CI adults data point
plotline <- ci.dat[1:2,]
plotline$subject<-"nl_CIK100"
plotline[plotline$dir_voice=="F0",]$threshold<-9.19
plotline[plotline$dir_voice=="VTL",]$threshold<-7.19
plotline$thrs.g.log<-log(plotline$threshold)
plotline$age<-19
plotline$expci<-19
plotline$group<-"CI Adults Gaudrain & Baskent (2018)"
ci.dat.2<-rbind(ci.dat, plotline)


#fig1
fig1 <- ggplot(ci.dat.2, aes(x = age, y = thrs.g.log, fill=group)) +
      geom_boxplot(data = nh.dat, aes(x = plot_age, y = thrs.g.log, 
      fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      outlier.shape = NA) + 
    geom_point(data=ci.dat.2, aes(x = age, y = thrs.g.log, color=group),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Log-transformed JND (st)", 
                     breaks = c(-2.3,-0.693,0,0.693,1.1,1.39,1.61, 2.3,2.71,3),
                     labels = c("0.1","0.5","1","2","3","4","5","10","15","20"), 
                     limits = c(-2.31, 3.09))+
  scale_x_continuous(name = "Chronological age (yrs)", breaks = c(2,4,6,8,10,12,14,16,19),
                     labels = c("2","4","6","8","10","12","14","16","Adults"),
                     limits = c(1.9,20.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6","#05668D","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#9E0059","#a4c49e","#033d54","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
  facet_wrap(~ dir_voice) +
#  geom_smooth(method="lm", data = nh.dat, aes(x = plot_age, y = thrs.g.log, fill = group),alpha = .15) + 
   geom_ribbon(data=datlm, 
               aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
                alpha = .15, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) +
   theme_bw() +
  theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.title = element_text(size=22, face="bold"),
        legend.position = "bottom")

# Show fig1
fig1


#fig1
fig1a <- ggplot(ci.dat.2, aes(x = age, y = thrs.g.log, fill=group)) +
      geom_boxplot(data = nh.dat, aes(x = plot_age, y = thrs.g.log, 
      fill = group), alpha=0.3, color="grey",show.legend = FALSE,
      outlier.shape = NA) + 
    geom_point(data=ci.dat.2, aes(x = age, y = thrs.g.log, color=group),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Log-transformed JND (st)", 
                     breaks = c(-2.3,-0.693,0,0.693,1.1,1.39,1.61, 2.3,2.71,3),
                     labels = c("0.1","0.5","1","2","3","4","5","10","15","20"), 
                     limits = c(-2.31, 3.09))+
  scale_x_continuous(name = "Chronological age (yrs)", breaks = c(2,4,6,8,10,12,14,16,19),
                     labels = c("2","4","6","8","10","12","14","16","Adults"),
                     limits = c(1.9,20.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6","#05668D","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#9E0059","#a4c49e","#033d54","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
  facet_wrap(~ dir_voice) +
#  geom_smooth(method="lm", data = nh.dat, aes(x = plot_age, y = thrs.g.log, fill = group),alpha = .15) + 
   geom_ribbon(data=datlm, 
               aes(ymin = lwr, ymax = upr, fill = NULL),
                alpha = .25, show.legend = FALSE, fill="grey") +
 # geom_line(data=datlm, aes(y = predlm), size = 1) +
   theme_bw() +
  theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.title = element_text(size=22, face="bold"),
        legend.position = "bottom")

# Show fig1
fig1a

#+geom_ribbon(aes(ymin=data$lower, ymax=data$upper), linetype=2, alpha=0.1)

#define variable expCI as numeric instead of character
dat$expci<-as.numeric(dat$expci)

#fig2
fig2 <- ggplot(ci.dat.2, aes(x = age, y = thrs.g.log, fill=group)) +
      geom_boxplot(data = nh.dat, aes(x = plot_age, y = thrs.g.log, 
      fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      outlier.shape = NA) + 
    geom_point(data=ci.dat.2, aes(x = expci, y = thrs.g.log,
                                    color=group),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Log-transformed JND (st)", 
                     breaks = c(-2.3,-0.693,0,0.693,1.1,1.39,1.61, 2.3,2.71,3),
                     labels = c("0.1","0.5","1","2","3","4","5","10","15","20"), 
                     limits = c(-2.31, 3.09))+
  scale_x_continuous(name = "Hearing age (yrs)", breaks = c(2,4,6,8,10,12,14,16,19),
                     labels = c("2","4","6","8","10","12","14","16","Adults"),
                     limits = c(1.9,20.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6","#05668D","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#9E0059","#a4c49e","#033d54","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
  facet_wrap(~ dir_voice) +
  geom_ribbon(data=datlm, 
               aes(ymin = lwr, ymax = upr, fill = group,
                   color = NULL),
                alpha = .15, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) + 
  theme_bw() +
  theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.title = element_text(size = 22, face="bold"))

# Show fig2
fig2


#fig2
fig2a <- ggplot(ci.dat.2, aes(x = age, y = thrs.g.log, fill=group)) +
      geom_boxplot(data = nh.dat, aes(x = plot_age, y = thrs.g.log, 
      fill = group), alpha=0.3, color="grey",show.legend = FALSE,
      outlier.shape = NA) + 
    geom_point(data=ci.dat.2, aes(x = expci, y = thrs.g.log,
                                    color=group),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Log-transformed JND (st)", 
                     breaks = c(-2.3,-0.693,0,0.693,1.1,1.39,1.61, 2.3,2.71,3),
                     labels = c("0.1","0.5","1","2","3","4","5","10","15","20"), 
                     limits = c(-2.31, 3.09))+
  scale_x_continuous(name = "Hearing age (yrs)", breaks = c(2,4,6,8,10,12,14,16,19),
                     labels = c("2","4","6","8","10","12","14","16","Adults"),
                     limits = c(1.9,20.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6","#05668D","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#9E0059","#a4c49e","#033d54","purple"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults","CI Adults Gaudrain & Baskent (2018)")) +
  facet_wrap(~ dir_voice) +
  geom_ribbon(data=datlm, 
               aes(ymin = lwr, ymax = upr, fill = NULL,
                   color = NULL),
                alpha = .25, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) + 
  theme_bw() +
  theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.title = element_text(size = 22, face="bold"))

# Show fig2
fig2a



CIs<-ggarrange(fig1,fig2,nrow=2,ncol=1,common.legend = TRUE, legend="bottom", labels="AUTO", font.label = list(size=22))

CIs

#annotate_figure(CIs,top = text_grob("F0 and VTL discrimination in CI children", color = "black", face = "bold", size = 16, hjust = .43, vjust = .2))

ggsave(file="Figure 1 - Fishy CI data.png", units = c("cm"), width = 35,height = 40, dpi = 600)
ggsave(file="Figure 1 - Fishy CI data.pdf", units = c("cm"), width = 35, height = 40, dpi = 600)


CIs.ASA<-ggarrange(fig1,fig2,nrow=1,ncol=2,common.legend = TRUE, legend="bottom")

CIs.ASA

annotate_figure(CIs.ASA, top = text_grob("Fig. 1", color = "black", face = "bold", size = 30))

ggsave(file="ASA Poster Fishy.png", units = c("cm"), width = 70,height = 28, dpi = 600)



```


# RQ1 - Check how developmental effect in CI children differs from NH children
``` {r lmer developmental effect}

options(digits=7)


# Full lmer model with interaction dir_voice*age*CI
Fishy_m0<-lmer(thrs.g.log ~ dir_voice*age*CI +
                 (1 |subject), 
           data=kid.dat, REML=FALSE)

save(Fishy_m0, file='Fishy_m0.Rdata')

# Lmer model with fixed effects of dir_voice*age + age*CI + dir_voice*CI
Fishy_m1<-lmer(thrs.g.log ~ dir_voice*age + age*CI + dir_voice*CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m1, file='Fishy_m1.Rdata')


# Three-way interaction dir_voice*age*CI does not improve the model
anova(Fishy_m1,Fishy_m0)


# Lmer model without dir_voice*age
Fishy_m2<-lmer(thrs.g.log ~ age*CI + dir_voice*CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m2, file='Fishy_m2.Rdata')

# Interaction dir_voice*age does not improve the model
anova(Fishy_m2,Fishy_m1)


# Lmer model without dir_voice*CI
Fishy_m3<-lmer(thrs.g.log ~ dir_voice*age + age*CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m3, file='Fishy_m3.Rdata')

# Interaction dir_voice*CI does improve the model
anova(Fishy_m3,Fishy_m1)
#Fishy_m3 has slightly better BIC value than Fishy_m2
anova(Fishy_m2, Fishy_m3)


# Lmer model without age*CI
Fishy_m4<-lmer(thrs.g.log ~ dir_voice*CI + dir_voice*age +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m4, file='Fishy_m4.Rdata')

# Interaction age*CI does not improve the model
anova(Fishy_m4,Fishy_m1)
#Fishy_m3 has slightly better BIC value than Fishy_m2 and Fishy_m4
anova(Fishy_m2, Fishy_m3, Fishy_m4)


# Lmer model without dir_voice*age
Fishy_m5<-lmer(thrs.g.log ~ dir_voice+ age*CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m5, file='Fishy_m5.Rdata')

# Interaction dir_voice*age does not improve the model
anova(Fishy_m3,Fishy_m5)


# Lmer model without age*CI
Fishy_m6<-lmer(thrs.g.log ~ dir_voice*age + CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m6, file='Fishy_m6.Rdata')


# Interaction age*CI does not improve the model
anova(Fishy_m6,Fishy_m3)

#Fishy_m5 has slightly better AIC and BIC values than Fishy_m6
anova(Fishy_m6, Fishy_m5)


# Lmer model without age*CI
Fishy_m7<-lmer(thrs.g.log ~ dir_voice + age + CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

# Interaction age*CI does not improve the model
anova(Fishy_m5,Fishy_m7)


# without dir_voice
# not better than m7
Fishy_m8<-lmer(thrs.g.log ~ age + CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m8, file='Fishy_m8.Rdata')

# Fixed effect of dir_voice does improve the model
anova(Fishy_m7,Fishy_m8)


# without age
# not better than m7
Fishy_m9<-lmer(thrs.g.log ~ dir_voice + CI +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m9, file='Fishy_m9.Rdata')

# Fixed effect of dir_voice does improve the model
anova(Fishy_m7,Fishy_m9)


# without CI
# not better than m7
Fishy_m10<-lmer(thrs.g.log ~ dir_voice + age +(1 |subject), 
                data=kid.dat, REML=FALSE)

save(Fishy_m10, file='Fishy_m10.Rdata')

# Fixed effect of dir_voice does improve the model
anova(Fishy_m7,Fishy_m10)




### Fishy_m7 is the best fitting model

# Look at coeffiCIents and p-values
anova(Fishy_m7)

summary(Fishy_m7)

### Intermediate conclusion ###

# - Children's JNDs develop at a similar rate/parallel and a similar manner with age for F0 and VTL. Children's JNDs were generally lower for VTL than for VTL. There are no speCIfic differences in how JNDs develop for F0 and VTL with age between NH and CI children but generally higher JNDs in CI children 



ci.dat$ageimp<-as.numeric(as.character(ci.dat$ageimp))

# Full lmer model with interaction dir_voice*age*CI
Fishy_ci_m0<-lmer(thrs.g.log ~ dir_voice+age + expci
                  + ageimp 
                  + (1 |subject), 
           data=ci.dat, REML=FALSE)



cor.test(x=ci.dat$age, 
         y=ci.dat$ageimp, method="pearson")

cor.test(x=ci.dat$age, 
         y=ci.dat$expci, method="pearson")


cor.test(x=ci.dat$ageimp, 
         y=ci.dat$expci, method="pearson")



```




# RQ2 - Check how development differs in CI from NH children
``` {r lmer adult-level performance}



# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/Desktop/CI Paper/Figures')


means <- summarySE(nh.dat, measurevar="thrs.g.log", groupvars=c("group","dir_voice"))



# 12-year old child will be considered 10-12 and older children as adults
ci.dat$group.new<-ci.dat$group
ci.dat[ci.dat$group.new=="12-14",]$group.new<-"10-12"
ci.dat[ci.dat$group.new=="14-17",]$group.new<-"adults"

ci.dat$mean<-0
ci.dat$sd<-0
groups<-unique(ci.dat$group.new)
cues<-unique(ci.dat$dir_voice)
subjects <- unique(ci.dat$subject)

for (i in groups){
  for (icue in cues) {
      ci.dat$mean<-
        ifelse(ci.dat$group.new==i & ci.dat$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$thrs.g.log,
        ci.dat$mean)
  }
}


for (i in groups){
  for (icue in cues) {
      ci.dat$sd<-
        ifelse(ci.dat$group.new==i & ci.dat$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$sd,
        ci.dat$sd)
  }
}

# calculate z-scores 
ci.dat$zscore<-0
ci.dat$zscore<-(ci.dat$thrs.g.log - ci.dat$mean)/ci.dat$sd



fig3 <- ggplot(ci.dat, aes(x = age, y = zscore, fill=group.new)) +
      # geom_boxplot(data = nh.dat, aes(x = plot_age, y = thrs.g.log, 
      # fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      # outlier.shape = NA) + 
    geom_point(data=ci.dat, aes(x = age, y = zscore, color=group.new),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Z-scores", limits = c(-2, 6.5), 
                     breaks = c(-2,0,2,4,6))+
  scale_x_continuous(name = "Chronological age (yrs)", breaks = c(2,4,6,8,10,12,14,16),
                     labels = c("2","4","6","8","10","12","14","16"),
                     limits = c(1.9,17.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#05668D"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#033d54"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
  facet_wrap(~ dir_voice) +
#  geom_smooth(method="lm", data = nh.dat, aes(x = plot_age, y = thrs.g.log, fill = group),alpha = .15) + 
   # geom_ribbon(data=datlm, 
   #             aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
   #              alpha = .15, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) + 
    geom_hline(yintercept=-1.96,linetype="dashed", color = "black") +
    geom_hline(yintercept=1.96,linetype="dashed", color = "black") +
    theme_bw() +
    theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        legend.title = element_text(size=22, face="bold"))

# Show fig1
fig3



# Same analysis for CI children's hearing age

#new hearing age groups
ci.dat$group.expci<-0
ci.dat$group.expci<-ifelse(ci.dat$expci<6,"04-06",ci.dat$group.expci)
ci.dat$group.expci<-ifelse(ci.dat$expci>=6 & ci.dat$expci<8,"06-08",ci.dat$group.expci)
ci.dat$group.expci<-ifelse(ci.dat$expci>=8 & ci.dat$expci<10,"08-10",ci.dat$group.expci)
ci.dat$group.expci<-ifelse(ci.dat$expci>=10 & ci.dat$expci<12.1,"10-12",ci.dat$group.expci)
ci.dat$group.expci<-ifelse(ci.dat$expci>12.1,"adults",ci.dat$group.expci)

ci.dat$mean.expci<-0
ci.dat$sd.expci<-0
groups<-unique(ci.dat$group.expci)
cues<-unique(ci.dat$dir_voice)
subjects <- unique(ci.dat$subject)

for (i in groups){
  for (icue in cues) {
      ci.dat$mean.expci<-
        ifelse(ci.dat$group.expci==i & ci.dat$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$thrs.g.log,
        ci.dat$mean.expci)
  }
}


for (i in groups){
  for (icue in cues) {
      ci.dat$sd.expci<-
        ifelse(ci.dat$group.expci==i & ci.dat$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$sd,
        ci.dat$sd.expci)
  }
}

# calculate z-scores hearing age
ci.dat$zscore.expci<-0
ci.dat$zscore.expci<-(ci.dat$thrs.g.log - ci.dat$mean.expci)/ci.dat$sd.expci



fig4 <- ggplot(ci.dat, aes(x = expci, y = zscore.expci, fill=group.expci)) +
      # geom_boxplot(data = nh.dat, aes(x = plot_age, y = thrs.g.log, 
      # fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      # outlier.shape = NA) + 
    geom_point(data=ci.dat, aes(x = expci, y = zscore.expci,
                                color=group.expci),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Z-scores", limits = c(-2, 6.5), 
                     breaks = c(-2,0,2,4,6))+
  scale_x_continuous(name = "Hearing age (yrs)", breaks = c(2,4,6,8,10,12,14,16),
                     labels = c("2","4","6","8","10","12","14","16"),
                     limits = c(1.9,17.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#05668D"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#033d54"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
  facet_wrap(~ dir_voice) +
#  geom_smooth(method="lm", data = nh.dat, aes(x = plot_age, y = thrs.g.log, fill = group),alpha = .15) + 
   # geom_ribbon(data=datlm, 
   #             aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
   #              alpha = .15, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) + 
    geom_hline(yintercept=-1.96,linetype="dashed", color = "black") +
    geom_hline(yintercept=1.96,linetype="dashed", color = "black") +
    theme_bw() +
    theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        legend.title = element_text(size=22, face="bold"))

# Show fig1
fig4


Zscores<-ggarrange(fig3,fig4,nrow=2,ncol=1,common.legend = TRUE, legend="bottom", labels="AUTO", font.label = list(size=22))

Zscores


ggsave(file="Figure 2 - Zscores Fishy.png", units = c("cm"), width = 25,height = 25, dpi = 600)
ggsave(file="Figure 2 - Zscores Fishy.pdf", units = c("cm"), width = 25, height = 25, dpi = 600)




```


# Check adult-like performance
``` {r lmer adult-level performance}
### Use CI data for this part. ###
adult.dat<-nh.dat[nh.dat$group=="adults",]
#adult.dat$subject<-droplevels(adult.dat$subject)
ci.dat<-dat[dat$CI=="CI",]

dat.dun<-rbind(ci.dat, adult.dat)

# Variable CI is a factor
dat.dun$CI<-as.factor(dat.dun$CI)
dat.dun$CI<-relevel(dat.dun$CI, ref="NH")
# Log-transformed thresholds
dat.dun$thrs.g.log<-log(dat.dun$threshold)
dat$thrs.g.log<-log(dat$threshold_geom)

# Relevel group and dir_voice reference levels to Adults and VTL
dat.dun$group<-as.factor(dat.dun$group)
dat.dun$group <- relevel(dat.dun$group, ref="adults")
dat.dun$dir_voice <- relevel(dat.dun$dir_voice, ref="F0")

### Dunnett Test with F0 and VTL ###
# Dunnett Test with F0
DunnettTest(thrs.g.log ~ group, data=dat.dun, subset=dat$dir_voice=="F0")

# Dunnett Test with VTL
DunnettTest(thrs.g.log ~ group, data=dat.dun, subset=dat$dir_voice=="VTL")

### Intermediate conclusion

# - For F0, there are differences between thresholds of Adults with all age groups of children.

# - For VTL, there are only differences between thresholds of Adults with children between 4 and 8. 


dat_f0<-dat[dat$dir_voice=="F0",]
dat_vtl<-dat[dat$dir_voice=="VTL",]

dat_f0_46 <- dat_f0[dat_f0$group=="4-6",]
dat_f0_68 <- dat_f0[dat_f0$group=="6-8",]
dat_f0_810 <- dat_f0[dat_f0$group=="8-10",]
dat_f0_1012 <- dat_f0[dat_f0$group=="10-12",]
dat_f0_Adults <- dat_f0[dat_f0$group=="Adults",]

# cohen.d(dat_f0_46$thrs.g.log, dat_f0_Adults$thrs.g.log)
# cohen.d(dat_f0_68$thrs.g.log, dat_f0_Adults$thrs.g.log)
# cohen.d(dat_f0_810$thrs.g.log, dat_f0_Adults$thrs.g.log)
# cohen.d(dat_f0_1012$thrs.g.log, dat_f0_Adults$thrs.g.log)
# 


dat_vtl_46 <- dat_vtl[dat_vtl$group=="4-6",]
dat_vtl_68 <- dat_vtl[dat_vtl$group=="6-8",]
dat_vtl_810 <- dat_vtl[dat_vtl$group=="8-10",]
dat_vtl_1012 <- dat_vtl[dat_vtl$group=="10-12",]
dat_vtl_Adults <- dat_vtl[dat_vtl$group=="Adults",]

# cohen.d(dat_vtl_46$thrs.g.log, dat_vtl_Adults$thrs.g.log)
# cohen.d(dat_vtl_68$thrs.g.log, dat_vtl_Adults$thrs.g.log)
# cohen.d(dat_vtl_810$thrs.g.log, dat_vtl_Adults$thrs.g.log)
# cohen.d(dat_vtl_1012$thrs.g.log, dat_vtl_Adults$thrs.g.log)
# 



```

