---
title: "CI Results Plot"
author: "Leanne Nagels"
date: "Generated on: `r date()`"
output: 
  html_document:
    toc: true
    code_folding: show
    toc_float: 
        collapsed: false
        smooth_scroll: true
    number_sections: false
---

# Description 
This R Markdown File can be used to plot results of CI children for the Gender experiment from the PICKA Project.

# Load packages and data
Load the required packages and download the required files. 

```{r setup, message=F, echo=F, eval=T}
# some custom options to generate a nice html file
options(digits = 3)
options(width=100)
library(knitr)
opts_chunk$set(cache=F, comment='#', tidy = T, tidy.opts=list(blank=T, width.cutoff=100), fig.align='center', message=T, warning=T, fig.width=8, fig.height=8, dev='png',eval=T)

# test if the necessary packages are installed if not, install them
packages <- c("ggplot2", "RColorBrewer", "reshape2","Rmisc","lmerTest","lme4","optimx","vctrs", "moments","ez","DescTools","optimx","ggpubr","ggnewscale")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())), repos='http://cran.us.r-project.org')  
}

# Load required packages
library(ggplot2)
library(RColorBrewer)
library(reshape2)
library(Rmisc)
library(lmerTest)
library(lme4)
library(optimx)
library(moments)
library(ez)
library(DescTools)
library(optimx)
library(ggpubr)
library(ggnewscale)
library(car)

# Set PICKA WD for CI data
# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/PICKA Experiments/')

# Read CSV file Results Gender
CI.dat<-read.csv('./Experiments/gender/results/gen_db_responses.csv',header=TRUE)

# Add variable for female responses
CI.dat$is_woman = CI.dat$response=='woman'

# Open demographics table with subject,age (yy;mm), group, gender, and vocabulary score
CI.dem<-read.table('demographsCI.txt', header=TRUE)
CI.dem$group<-revalue(CI.dem$group, c("04-06"="4-6", "06-08"="6-8", "08-10"="8-10", "10-12"="10-12", "12-14"="12-14", "14-17"="14-17"))


CI.dem$group<-factor(CI.dem$group, levels=c("4-6","6-8","8-10","10-12", "12-14", "14-17"))


# Merge dataframes
CI.dat<-merge.data.frame(CI.dat,CI.dem, by='subject')

#CI.dat$subject<-droplevels(CI.dat$subject)

# Leave out partial data from subject nl_CIK009 
CI.dat<-CI.dat[CI.dat$subject!="nl_CIK009",]


### Set PICKA WD for NH data
# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/PICKA Experiments_NH/')

# Read CSV file Results Gender
nh.dat<-read.csv('./Experiments/gender/results/gen_db_responses.csv',header=TRUE)

# Add variable for female responses
nh.dat$is_woman = nh.dat$response=='woman'

# Open demographics table with subject,age (yy;mm), group, gender, and vocabulary score
nh.dem<-read.table('demographs.txt', header=TRUE)

nh.dem$group<-revalue(nh.dem$group, c("04-06"="4-6", "06-08"="6-8", "08-10"="8-10", "10-12"="10-12", "12-14"="12-14", "14-17"="14-17","adults"="Adults"))

nh.dem$group<-factor(nh.dem$group, levels=c("4-6","6-8","8-10","10-12","12-14", "14-17","Adults"))

# Merge dataframes
nh.dat<-merge.data.frame(nh.dat,nh.dem, by='subject')

# no UK or CI partiCIpants in NH datastruct
nh.dat <- nh.dat[grepl('gb',nh.dat$subject)!=1,]
nh.dat <- nh.dat[grepl('CI',nh.dat$subject)!=1,]


#nh.dat$subject <- droplevels(nh.dat$subject)

#create same number of variables to merge data frames
nh.dat$expci <- '-'

#add variable to identify CI and NH groups
CI.dat$CI<-"CI"
nh.dat$CI<-"NH"

#merge data frames
dat<-rbind(CI.dat, nh.dat)

# Variable CI is a factor
dat$CI<-as.factor(dat$CI)
dat$CI<-relevel(dat$CI, ref="NH")


#Add exp CI variable for CI children
dat$expci<-0
subjects<-unique(CI.dat$subject)
for (i in subjects){
dat[dat$subject==i,]$expci<-CI.dem[CI.dem$subject==i,]$expci
}



```


# Information data

```{r lookat}
#head(dat)
#str(dat)
#summary(dat)


# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/Desktop/CI Paper/Figures')


# Normalize f0 and vtl differences
dat$df0_norm<-(-(dat$df0/12)-0.5)
dat$dvtl_norm<-(dat$dvtl/3.6)-0.5


# Log-transform age 
dat$age_log = log(dat$age)


```


# New analysis BK units
``` {r Bk units conversion}


# Coefficients for F0
Gen_coef <- glmer(is_woman ~ (df0_norm+dvtl_norm|subject), 
                  data = dat, 
                  family=binomial,
                  control = glmerControl(optimizer="optimx",
                                                 optCtrl =
                                                list(method="nlminb")))

coef(Gen_coef)


# store cue weights for df0_norm and dvtl_norm
c <- coef(Gen_coef)$subject
c$subject <- rownames(c)
c$df0_norm_coef<-c$df0_norm
c$dvtl_norm_coef<-c$dvtl_norm
c$df0_norm<-NULL
c$dvtl_norm<-NULL

head(c)


# Add df0_norm and dvtl_norm coefficients to dat dataframe
dat<-merge.data.frame(dat,c, by='subject')

# Add dem to c dataframe
c<-merge.data.frame(c, nh.dem, by='subject')

#add variable to identify CI and NH groups
c$CI<-"NA"
c[grepl('CI',c$subject)==1,]$CI<-"CI"
c[grepl('NH',c$subject)==1,]$CI<-"NH"


#Add expCI variable for CI children
c$expci<-0
subjects<-unique(c[c$CI=="CI",]$subject)
for (i in subjects){
c[c$subject==i,]$expci<-CI.dem[CI.dem$subject==i,]$expci
}


# Convert coefficients to BK units
c$df0_bk <- -(c$df0_norm_coef/(12*log(2)))
c$dvtl_bk <- -(c$dvtl_norm_coef/(3.6*log(2)))

# Make dataframe to plot in one figure
c.1<-c[rep(1:nrow(c),each=2),]
c.1$dir_voice<-c("F0","VTL")
c.1$dir_voice<-as.factor(c.1$dir_voice)
c.1$bk<-0
c.1[c.1$dir_voice=="F0",]$bk<-c.1[c.1$dir_voice=="F0",]$df0_bk
c.1[c.1$dir_voice=="VTL",]$bk<-c.1[c.1$dir_voice=="VTL",]$dvtl_bk

# Add plot age variable for plot
c.1$plot_age<-c.1$age
c.1[c.1$group=="Adults",]$plot_age <- c(18.1, 18.3, 18.5, 18.6, 18.7, 18.8, 18.9, 19, 19.1, 19.2, 19.3, 19.4, 19.5, 19.7, 19.9)


# # Add dem to c dataframe
# c.f0<-merge.data.frame(c.f0, nh.dem, by='subject')
# c.vtl<-merge.data.frame(c.vtl, nh.dem, by='subject')

# Add variable CI to indicate group
c.1$CI<-0
c.1[grepl('CI',c.1$subject)==1,]$CI<-"CI"
c.1[grepl('NH',c.1$subject)==1,]$CI<-"NH"


#Add expCI variable for CI children
c.1$expci<-0
subjects<-unique(c.1[c.1$CI=="CI",]$subject)
for (i in subjects){
c.1[c.1$subject==i,]$expci<-CI.dem[CI.dem$subject==i,]$expci
}


#revalue group for plotting, weird unsolved bug
c.1$group<-revalue(c.1$group, c("4-6"="04-06", "6-8"="06-08", "8-10"="08-10", "10-12"="10-12", "12-14"="12-14", "14-17"="14-17","Adults" = "Adults"))


# only coefficients of NH
c.1.nh<-c.1[c.1$CI=="NH",]
# only coefficients of NH kids
c.1.nh.kid<-c.1.nh[c.1.nh$group!="Adults",]


fitlm = lm(bk ~ age*dir_voice, data = c.1.nh.kid)
c.1.nh.kid$predlm = predict(fitlm)
predslm = predict(fitlm, interval = "prediction",level=0.5)
datlm = cbind(c.1.nh.kid, predslm)


c.1$bk<-as.numeric(c.1$bk)
datlm$bk<-as.numeric(datlm$bk)

setwd('C:/Users/leann/Desktop/CI Paper/Figures')

# Improvement 
fig3a <- ggplot(c.1, aes(x = plot_age, y = bk, fill =group)) +
geom_boxplot(data=c.1[c.1$CI=="NH",], aes(x = plot_age, y = bk, 
      fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      outlier.shape = NA) +
geom_point(data=c.1[c.1$CI=="CI",], aes(x = age, y = bk, color=group),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
scale_y_continuous(name = "Cue weight (Bk/st)", breaks = c(0.0, 1.5, 2.5)) + 
  scale_x_continuous(name = "Chronological age (yrs)", breaks = c(2,4,6,8,10,12,14,16,19),
                     labels = c("2","4","6","8","10","12","14","16","Adults"),
                     limits = c(1.9,20.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6","#05668D"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#9E0059","#a4c49e","#033d54"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults")) +
  facet_wrap(~ dir_voice) +
 # geom_hline(yintercept=mean(c.1$bk), linetype="dashed", color = "black") +
  geom_ribbon(data=datlm, 
               aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
                alpha = .15, show.legend = FALSE) +
  ggtitle("F0 and VTL weighting coeffiCIents") +
  theme_bw() +
  theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        legend.title = element_text(size=22, face="bold"))
# Show plot
fig3a



#new hearing age groups
c.1$group.expci<-0
c.1[c.1$CI=="CI" & c.1$expci>= 4 & c.1$expci<6,]$group.expci<- "04-06"
c.1[c.1$CI=="CI" & c.1$expci>=6 & c.1$expci<8,]$group.expci<- "06-08"
c.1[c.1$CI=="CI" & c.1$expci>=8 & c.1$expci<10,]$group.expci<- "08-10"
c.1[c.1$CI=="CI" & c.1$expci>=10 & c.1$expci<12,]$group.expci<- "10-12"
c.1[c.1$CI=="CI" & c.1$expci>=12 & c.1$expci<14,]$group.expci<- "12-14"
c.1[c.1$CI=="CI" & c.1$expci>=14 & c.1$expci<17,]$group.expci<- "14-17"
#c.1[c.1$CI=="CI" & c.1$expci>17.1,]$group.expci<- "Adults"

fig3b <- ggplot(c.1, aes(x = age, y = bk, fill =group)) +
geom_boxplot(data=c.1[c.1$CI=="NH",], aes(x = plot_age, y = bk, 
      fill = group), alpha=0.1, color="grey",
      show.legend = FALSE,outlier.shape = NA) +
geom_point(data=c.1[c.1$CI=="CI",], aes(x = expci, y = bk, color=group, fill=group),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
scale_y_continuous(name = "Cue weight (Bk/st)", breaks = c(-1.0, 0.0, 1.5, 2.5)) + 
  scale_x_continuous(name = "Hearing age (yrs)", breaks = c(2,4,6,8,10,12,14,16,19),
                     labels = c("2","4","6","8","10","12","14","16","Adults"),
                     limits = c(1.9,20.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6","#05668D"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#9E0059","#a4c49e","#033d54"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs","Adults")) +
  facet_wrap(~ dir_voice) +
  geom_ribbon(data=datlm, 
               aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
                alpha = .15, show.legend = FALSE) +
  ggtitle("F0 and VTL weighting coefficients") +
  theme_bw() +
  theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        legend.title = element_text(size=22, face="bold"))
# Show boxplot F
fig3b



CIs<-ggarrange(fig3a,fig3b,nrow=2,ncol=1,common.legend = TRUE, legend="bottom", labels="AUTO", font.label = list(size=22))

CIs


ggsave(file="Figure 3 - Gender CI data.png", units = c("cm"), width = 28,height = 35, dpi = 600)
ggsave(file="Figure 3 - Gender CI data.pdf", units = c("cm"), width = 28, height = 35, dpi = 600)


# CIs.ASA<-ggarrange(fig3a,fig3b,nrow=1,ncol=2,common.legend = TRUE, legend="bottom")
# 
# annotate_figure(CIs.ASA, top = text_grob("Fig. 2", color = "black", face = "bold", size = 30))
# 
# 
# ggsave(file="ASA Poster Gender Bks.png", units = c("cm"), width = 70,height = 28, dpi = 600)
# 
# 


#ggsave(file="Gen_coefficients.jpg", units = c("cm"),dpi = 300)


```



# RQ1 - Check developmental effect
``` {r lmer developmental effect}

c.1$age_log<-log(c.1$age)
c.1.kids<-c.1[c.1$group!="Adults",]
#c.1.kids$group<-droplevels(c.1.kids$group)

# Full lmer model with interaction dir_voice*age*CI
Gender_m0 <- lmer(bk ~ dir_voice*age_log*CI + (1|subject),
                   data = c.1.kids, REML=FALSE)

#save(Gender_m0, file='Gender_m0.Rdata')


# Lmer model with fixed effects of dir_voice*age + age*CI + dir_voice*CI
Gender_m1<-lmer(bk ~ dir_voice*age + age*CI + dir_voice*CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)

#save(Gender_m1, file='Gender_m1.Rdata')


# Three-way interaction dir_voice*age*CI does not improve the model
anova(Gender_m1,Gender_m0)


# Lmer model without dir_voice*age
Gender_m2<-lmer(bk ~ age*CI + dir_voice*CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)

#save(Gender_m2, file='Gender_m2.Rdata')

# Interaction dir_voice*age does not significantly improve the model
anova(Gender_m2,Gender_m1)


# Lmer model without age*CI
Gender_m3<-lmer(bk ~ dir_voice*age + dir_voice*CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)

#save(Gender_m3, file='Gender_m3.Rdata')

# Interaction age*CI does not significantly improve the model
anova(Gender_m3,Gender_m1)


# Lmer model without dir_voice*CI
Gender_m4<-lmer(bk ~ dir_voice*age + age*CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)
#save(Gender_m4, file='Gender_m4.Rdata')

# Interaction dir_voice*CI does not significantly improve the model
anova(Gender_m4,Gender_m1)

# Continue with Model M4
anova(Gender_m1, Gender_m2, Gender_m3, Gender_m4)



# Lmer model without dir_voice*age
Gender_m5<-lmer(bk ~ dir_voice + age*CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)
#save(Gender_m5, file='Gender_m5.Rdata')

# Interaction dir_voice*age significantly improves the model, i.e., model fit is significantly worse without it.
anova(Gender_m4,Gender_m5)



# Lmer model without age*CI
Gender_m6<-lmer(bk ~ dir_voice*age + CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)
#save(Gender_m6, file='Gender_m6.Rdata')

# Interaction age*CI does not significantly improve the model
anova(Gender_m4,Gender_m6)


#Continue with Model M6

# Lmer model without dir_voice*age
Gender_m7<-lmer(bk ~ dir_voice + age + CI +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)
#save(Gender_m7, file='Gender_m7.Rdata')

# Interaction dir_voice*age significantly improves the model!
anova(Gender_m7,Gender_m6)


# Lmer model without CI
Gender_m8<-lmer(bk ~ dir_voice*age +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)
#save(Gender_m8, file='Gender_m8.Rdata')

# Effect of CI does not significantly improve the model!
anova(Gender_m8,Gender_m6)


# Lmer model without dir_voice*age
Gender_m9<-lmer(bk ~ dir_voice + age +
                  (1|subject),
                   data = c.1.kids, REML=FALSE)
#save(Gender_m9, file='Gender_m9.Rdata')

# Interaction dir_voice*age significantly improves the model!
anova(Gender_m9,Gender_m8)



### Gender_m8 is the best fitting model

# Look at coefficients and p-values
Anova(Gender_m8)

summary(Gender_m8)

### Intermediate conclusion ###

# - Children's weighting increases more with age for VTL than for F0. 


# calculate weight ratios
ratio.adults <- mean(c.1[c.1$group=="Adults",]$df0_norm_coef/c.1[c.1$group=="Adults",]$dvtl_norm_coef)

ratio.kids <- mean(c.1[c.1$group!="Adults",]$df0_norm_coef/c.1[c.1$group!="Adults",]$dvtl_norm_coef)

ratio.kids/ratio.adults


ratio.adults.f0 <- mean(c.1[c.1$group=="Adults",]$df0_norm_coef)
ratio.adults.vtl <- mean(c.1[c.1$group=="Adults",]$dvtl_norm_coef)


ratio.kids.f0 <- mean(c.1[c.1$group!="Adults",]$df0_norm_coef)
ratio.kids.vtl <- mean(c.1[c.1$group!="Adults",]$dvtl_norm_coef)


# add variable that represents the ratio between F0 and VTL weighting 
c.1$ratio<-c.1$df0_norm_coef/c.1$dvtl_norm_coef

# set reference level of group to Adults
c.1$group<-relevel(c.1$group, ref = "Adults")

# perform Dunnett's test on subsets of F0 and VTL cues
# significant difference only for 4-6 year-olds and adults
DunnettTest(bk~group,data=c.1[c.1$dir_voice=="F0",])
# significant difference for 4-6, 6-8, 8-10 year-olds and adults
DunnettTest(bk~group,data=c.1[c.1$dir_voice=="VTL",])

# perform Dunnett's test on the ratio between F0 and VTL
# no differences in ratio between groups
DunnettTest(ratio~group,data=c.1[seq(1,nrow(c.1),2),])

# perform Dunnett's test on the intercepts
# intercepts are all significantly different for each group
DunnettTest(`(Intercept)`~group,data=c.1[seq(1,nrow(c.1),2),])




```


# Gradient plot
``` {r gradient plot}

# Upload Fuller et al. (2014) data
setwd('C:/Users/leann/Downloads/Fuller_etal_2014')

# Read data
Fuller.dat<-read.csv('./Fuller_etal_2014_JARO.csv',header=TRUE)
head(Fuller.dat)

# Select data from only CI adults
Fuller.dat.ci<-Fuller.dat[Fuller.dat$grp=="CI",]

# Select data from only conditions that were tested in this study, e.g. F0 0st, 6st, and 12st and VTL 1.00
Fuller.dat.ci.clean<-Fuller.dat.ci[Fuller.dat.ci$f0==0|Fuller.dat.ci$f0==6|Fuller.dat.ci$f0==12,]

Fuller.dat.ci.clean$df0<-0
Fuller.dat.ci.clean[Fuller.dat.ci.clean$f0==12,]$df0<- -12
Fuller.dat.ci.clean[Fuller.dat.ci.clean$f0==6,]$df0<- -6
Fuller.dat.ci.clean[Fuller.dat.ci.clean$f0==0,]$df0<-0

Fuller.dat.ci.clean<-Fuller.dat.ci.clean[Fuller.dat.ci.clean$vtl==1.00|Fuller.dat.ci.clean$vtl==0.91|Fuller.dat.ci.clean$vtl==0.81,]

# Convert to st
Fuller.dat.ci.clean$dvtl<-0
Fuller.dat.ci.clean[Fuller.dat.ci.clean$vtl==1.00,]$dvtl<-0.0
Fuller.dat.ci.clean[Fuller.dat.ci.clean$vtl==0.91,]$dvtl<-1.8
Fuller.dat.ci.clean[Fuller.dat.ci.clean$vtl==0.81,]$dvtl<-3.6

# Add variable is_woman
Fuller.dat.ci.clean$is_woman<-"FALSE"
Fuller.dat.ci.clean[Fuller.dat.ci.clean$response=="woman",]$is_woman<-"TRUE"

Fuller.dat.ci.clean$is_woman<-as.logical(as.character(Fuller.dat.ci.clean$is_woman))

Fuller.dat.ci.clean$group<-"CI Adults"
Fuller.dat.ci.clean$group.names<-"CI Adults"

Fuller.dat.ci.clean$group<-as.factor(as.character(Fuller.dat.ci.clean$group))
Fuller.dat.ci.clean$group.names<-as.factor(as.character(Fuller.dat.ci.clean$group.names))


# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/Desktop/CI Paper/Figures')



CI.dat$group.names<-revalue(CI.dat$group, c("4-6"="4-6 yrs", "6-8"="6-8 yrs", "8-10"="8-10 yrs", "10-12"="10-12 yrs","12-14"="12-14 yrs", "14-17"="14-17 yrs"))


CI.dat$subject.names<-CI.dat$subject
CI.dat$subject.names<-sub("nl_","",CI.dat$subject.names)


fig4a<-ggplot(data=aggregate(is_woman~df0+dvtl+subject+
              subject.names+group+                    group.names, subset(CI.dat), FUN=mean)) +
    geom_raster(aes(x=df0, y=dvtl, fill=is_woman)) +
    scale_fill_viridis_c(NULL, begin=0, end=1, option="C", guide=guide_colourbar(barheight=10, barwidth=2), limits=c(0,1), breaks=c(0,.25, .5, .75, 1), labels=c('Man (%)', '', '', '', 'Woman (%)')) +
    facet_wrap(~group.names+subject.names, ncol=7) +
    scale_x_continuous("F0 (st)", breaks=sort(unique(dat$df0)), labels=function(x){ format(x, digits=1) }) +
    scale_y_reverse("VTL (st)", breaks=c(0.0,1.8,3.6), labels=function(x){ format(x, digits=2) }) +
    #guides(fill=F) +
    theme_bw() +
    theme(aspect.ratio = 1) +
    theme(strip.background = element_blank(), 
          text = element_text(size = 22),
          strip.text = element_text(size = 20, face="bold"),
          axis.title = element_text(size=24, face="bold"),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, 
                                                      b = 0, l = 0)),
          axis.title.x = element_text(margin = margin(t = 20, r = 0, 
                                                      b = 0, l = 0)),
          axis.text.x=element_text(size = 22),
          axis.text.y=element_text(size = 22),
          legend.text = element_text(size = 22),
          panel.spacing.y = unit(1, "lines"),
          legend.title = element_text(size=22, hjust=.5))

fig4a


#ggsave(filename='Figure 4A - Gender Gradient CI.png', units = c("cm"), width = 28,height = 35, dpi=600)



s = summarySE(data=nh.dat, measurevar='is_woman', groupvars=c('dvtl', 'df0', 'group'))

s2 = summarySE(data=Fuller.dat.ci.clean, measurevar='is_woman', groupvars=c('dvtl', 'df0', 'group'))

s.all<-rbind(s,s2)

s.all$group.names<-revalue(s.all$group, c("4-6"="4-6 yrs", "6-8"="6-8 yrs", "8-10"="8-10 yrs", "10-12"="10-12 yrs","12-14"="12-14 yrs", "14-17"="14-17 yrs", "Adults"="Adults", "CI Adults"="CI Adults \nFuller et al. (2014)"))


fig4b <-ggplot(data=s.all) +
  geom_raster(aes(x=df0, y=dvtl, fill=is_woman)) +
  scale_fill_viridis_c(NULL, begin=0, end=1, option="C", guide=guide_colourbar(barheight=10, barwidth=2), limits=c(0,1), breaks=c(0,.25, .5, .75, 1), labels=c('Man', '', '', '', 'Woman')) +
  facet_grid(cols=vars(group.names)) +
  scale_x_continuous("F0 (st)", breaks=sort(unique(dat$df0)), labels=function(x){ format(x, digits=1) }) +
  scale_y_reverse("VTL (st)", breaks=sort(unique(dat$dvtl)), labels=function(x){ format(x, digits=2) }) +
    theme_bw() +
    theme(aspect.ratio = 1) +
    theme(strip.background = element_blank(), 
          text = element_text(size = 22),
          strip.text = element_text(size = 20, face="bold"),
          axis.title = element_text(size=24, face="bold"),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, 
                                                      b = 0, l = 0)),
          axis.title.x = element_text(margin = margin(t = 20, r = 0, 
                                                      b = 0, l = 0)),
          axis.text.x=element_text(size = 22),
          axis.text.y=element_text(size = 22),
          legend.text = element_text(size = 22),
          legend.title = element_text(size=22, hjust=.5))

fig4b

#ggsave(filename='Figure 4b - Gender Gradient NH.png', units = c("cm"), width = 28,height = 8, dpi=600)


Gradients<-ggarrange(fig4a,fig4b,nrow=2,ncol=1,common.legend = TRUE, labels="AUTO", legend = "right", font.label = list(size=22), heights = c(1.8,0.8), widths = c(1,1.1))

Gradients
ggsave(filename='Figure 4 - Gender Gradient Plots.png', units = c("cm"), width = 46,height = 35, dpi=600)








fig4a.ASA<-ggplot(data=aggregate(is_woman~df0+dvtl+subject + subject.names
            +group+group.names, subset(CI.dat), FUN=mean)) +
    geom_raster(aes(x=df0, y=dvtl, fill=is_woman)) +
    scale_fill_viridis_c(NULL, begin=0, end=1, option="C", guide=guide_colourbar(barheight=10, barwidth=2), limits=c(0,1), breaks=c(0,.25, .5, .75, 1), labels=c('Man (%)', '', '', '', 'Woman (%)')) +
    facet_wrap(~group.names+subject.names, ncol=5) +
    scale_x_continuous("F0 (st)", breaks=sort(unique(dat$df0)), labels=function(x){ format(x, digits=1) }) +
    scale_y_reverse("VTL (st)", breaks=c(0.0,1.8,3.6), labels=function(x){ format(x, digits=2) }) +
    #guides(fill=F) +
    theme_bw() +
    theme(aspect.ratio = 1) +
    theme(strip.background = element_blank(), 
          text = element_text(size = 22),
          strip.text = element_text(size = 20, face="bold"),
          axis.title = element_text(size=24, face="bold"),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, 
                                                      b = 0, l = 0)),
          axis.title.x = element_text(margin = margin(t = 20, r = 0, 
                                                      b = 0, l = 0)),
          axis.text.x=element_text(size = 22),
          axis.text.y=element_text(size = 22),
          legend.text = element_text(size = 22),
          panel.spacing.y = unit(1, "lines"),
          legend.title = element_text(size=22, hjust=.5))

fig4a.ASA


Gradients_Poster<-ggarrange(fig4a.ASA,fig4b,nrow=2,ncol=1,common.legend = TRUE, legend = "right", heights = c(2,0.8), widths = c(2,0.8))

annotate_figure(Gradients_Poster, top = text_grob("Fig. 3", color = "black", face = "bold", size = 30))


ggsave(filename='ASA Poster Gradients.png', units = c("cm"), width = 70,height = 28, dpi=600)



ASA<-ggarrange(fig3a,Gradients_Poster,nrow=1,ncol=2,common.legend = FALSE, heights = c(0.8,1), widths = c(0.8,1), font.label = list(size=22))

ggsave(filename='ASA Poster Gender.png', units = c("cm"), width = 70,height = 28, dpi=600)


```






# RQ2 - Check how development differs in CI from NH children
``` {r lmer adult-level performance}

# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/Desktop/CI Paper/Figures')

c.nh<-c[c$CI=="NH",]
c.ci<-c[c$CI=="CI",]

# Subset NH participants coefficients
# Make dataframe to plot in one figure and have two rows per participant
c.nh.2<-c.nh[rep(1:nrow(c.nh),each=2),]
c.nh.2$dir_voice<-c("F0","VTL")
c.nh.2$dir_voice<-as.factor(c.nh.2$dir_voice)
c.nh.2$bk<-0
c.nh.2[c.nh.2$dir_voice=="F0",]$bk<-c.nh.2[c.nh.2$dir_voice=="F0",]$df0_bk
c.nh.2[c.nh.2$dir_voice=="VTL",]$bk<-c.nh.2[c.nh.2$dir_voice=="VTL",]$dvtl_bk


# #revalue group for plotting, weird unsolved bug
c.nh.2$group<-revalue(c.nh.2$group, c("4-6"="04-06", "6-8"="06-08", "8-10"="08-10", "10-12"="10-12"))

means <- summarySE(c.nh.2, measurevar="bk", groupvars=c("group","dir_voice"))


# Subset CI children's coefficients
c.ci<-c[c$CI=="CI",]
# Make dataframe to plot in one figure and have two rows per participant
c.ci.2<-c.ci[rep(1:nrow(c.ci),each=2),]
c.ci.2$dir_voice<-c("F0","VTL")
c.ci.2$dir_voice<-as.factor(c.ci.2$dir_voice)
c.ci.2$bk<-0
c.ci.2[c.ci.2$dir_voice=="F0",]$bk<-c.ci.2[c.ci.2$dir_voice=="F0",]$df0_bk
c.ci.2[c.ci.2$dir_voice=="VTL",]$bk<-c.ci.2[c.ci.2$dir_voice=="VTL",]$dvtl_bk

# #revalue group for plotting, weird unsolved bug
 c.ci.2$group<-revalue(c.ci.2$group, c("4-6"="04-06", "6-8"="06-08", "8-10"="08-10", "10-12"="10-12"))


# 12-year old child will be considered 10-12 and older children as adults
c.ci.2$group.new<-c.ci.2$group
c.ci.2[c.ci.2$group.new=="12-14",]$group.new<-"10-12"
c.ci.2[c.ci.2$group.new=="14-17",]$group.new<-"Adults"
#c.ci.2$group.new<-droplevels(c.ci.2$group.new)

c.ci.2$mean<-0
c.ci.2$sd<-0
groups<-unique(c.ci.2$group.new)
cues<-unique(c.ci.2$dir_voice)
subjects <- unique(c.ci.2$subject)

for (i in groups){
  for (icue in cues) {
      c.ci.2$mean<-
        ifelse(c.ci.2$group.new==i & c.ci.2$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$bk,
        c.ci.2$mean)
  }
}


for (i in groups){
  for (icue in cues) {
      c.ci.2$sd<-
        ifelse(c.ci.2$group.new==i & c.ci.2$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$sd,
        c.ci.2$sd)
  }
}

# calculate z-scores 
c.ci.2$zscore<-0
c.ci.2$zscore<-(c.ci.2$bk - c.ci.2$mean)/c.ci.2$sd



fig3 <- ggplot(c.ci.2, aes(x = age, y = zscore, fill=group.new)) +
      # geom_boxplot(data = nh.dat, aes(x = plot_age, y = bk, 
      # fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      # outlier.shape = NA) + 
    geom_point(data=c.ci.2, aes(x = age, y = zscore, color=group.new),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Z-scores", limits = c(-2, 3.5), 
                     breaks = c(-2,0,2,4,6))+
  scale_x_continuous(name = "Chronological age (yrs)", breaks = c(2,4,6,8,10,12,14,16),
                     labels = c("2","4","6","8","10","12","14","16"),
                     limits = c(1.9,17.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#05668D"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#033d54"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
  facet_wrap(~ dir_voice) +
#  geom_smooth(method="lm", data = nh.dat, aes(x = plot_age, y = bk, fill = group),alpha = .15) + 
   # geom_ribbon(data=datlm, 
   #             aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
   #              alpha = .15, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) + 
    geom_hline(yintercept=-1.96,linetype="dashed", color = "black") +
    geom_hline(yintercept=1.96,linetype="dashed", color = "black") +
    theme_bw() +
    theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        legend.title = element_text(size=22, face="bold"))

# Show fig1
fig3



# Same analysis for CI children's hearing age

#new hearing age groups
c.ci.2$group.expci<-0
c.ci.2$group.expci<-ifelse(c.ci.2$expci<6,"04-06",c.ci.2$group.expci)
c.ci.2$group.expci<-ifelse(c.ci.2$expci>=6 & c.ci.2$expci<8,"06-08",c.ci.2$group.expci)
c.ci.2$group.expci<-ifelse(c.ci.2$expci>=8 & c.ci.2$expci<10,"08-10",c.ci.2$group.expci)
c.ci.2$group.expci<-ifelse(c.ci.2$expci>=10 & c.ci.2$expci<12.1,"10-12",c.ci.2$group.expci)
c.ci.2$group.expci<-ifelse(c.ci.2$expci>12.1,"Adults",c.ci.2$group.expci)

c.ci.2$mean.expci<-0
c.ci.2$sd.expci<-0
groups<-unique(c.ci.2$group.expci)
cues<-unique(c.ci.2$dir_voice)
subjects <- unique(c.ci.2$subject)

for (i in groups){
  for (icue in cues) {
      c.ci.2$mean.expci<-
        ifelse(c.ci.2$group.expci==i & c.ci.2$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$bk,
        c.ci.2$mean.expci)
  }
}


for (i in groups){
  for (icue in cues) {
      c.ci.2$sd.expci<-
        ifelse(c.ci.2$group.expci==i & c.ci.2$dir_voice==icue,
        means[means$group==i & means$dir_voice==icue,]$sd,
        c.ci.2$sd.expci)
  }
}

# calculate z-scores hearing age
c.ci.2$zscore.expci<-0
c.ci.2$zscore.expci<-(c.ci.2$bk - c.ci.2$mean.expci)/c.ci.2$sd.expci



fig4 <- ggplot(c.ci.2, aes(x = expci, y = zscore, fill=group.expci)) +
      # geom_boxplot(data = nh.dat, aes(x = plot_age, y = bk, 
      # fill = group), alpha=0.1, color="grey",show.legend = FALSE,
      # outlier.shape = NA) + 
    geom_point(data=c.ci.2, aes(x = expci, y = zscore,
                                color=group.expci),
         position=position_jitter(width=0.1,height=0),
         alpha=1,
         size=4,
         shape=21,
         colour="black",
         show.legend=TRUE) +
  scale_y_continuous(name = "Z-scores", limits = c(-2, 3.5), 
                     breaks = c(-2,0,2,4,6))+
  scale_x_continuous(name = "Hearing age (yrs)", breaks = c(2,4,6,8,10,12,14,16),
                     labels = c("2","4","6","8","10","12","14","16"),
                     limits = c(1.9,17.1)) +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#05668D"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
    scale_color_manual(name = "Age groups", values = c("#006970", "#8a6e00", "#972e04","#905100","#033d54"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","Adults")) +
  facet_wrap(~ dir_voice) +
#  geom_smooth(method="lm", data = nh.dat, aes(x = plot_age, y = bk, fill = group),alpha = .15) + 
   # geom_ribbon(data=datlm, 
   #             aes(ymin = lwr, ymax = upr, fill = group, color = NULL),
   #              alpha = .15, show.legend = FALSE) +
 # geom_line(data=datlm, aes(y = predlm), size = 1) + 
    geom_hline(yintercept=-1.96,linetype="dashed", color = "black") +
    geom_hline(yintercept=1.96,linetype="dashed", color = "black") +
    theme_bw() +
    theme(plot.title = element_blank(),
        text = element_text(size = 22),
        strip.text = element_text(size = 22),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 22),
        axis.text.y=element_text(size = 22),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        legend.title = element_text(size=22, face="bold"))

# Show fig1
fig4


Zscores<-ggarrange(fig3,fig4,nrow=2,ncol=1,common.legend = TRUE, legend="bottom", labels="AUTO", font.label = list(size=22))

Zscores


ggsave(file="Figure 5 - Zscores Gender.png", units = c("cm"), width = 25,height = 25, dpi = 600)
ggsave(file="Figure 5 - Zscores Gender.pdf", units = c("cm"), width = 25, height = 25, dpi = 600)




```



# RQ5 - Check correlation JNDs and weighting F0 and VTL
``` {r glmer correlation}


# Set PICKA WD for CI data
# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/PICKA Experiments/')

# Read CSV file Results Fishy
fishy.dat<-read.csv('./Experiments/fishy/results/jvo_db_results.csv',header=TRUE)

# no UK partiCIpants in datastruct
fishy.dat <- fishy.dat[grepl('gb',fishy.dat$subject)!=1,]


# Exclude some partiCIpants
# hearing thresholds too high for normal-hearing criteria
fishy.dat <- fishy.dat[fishy.dat$subject!="nl_NHA001",]
# test run
fishy.dat <- fishy.dat[fishy.dat$subject!="nl_NHK100",]
# incorrect comprehension of the task, only female responses
fishy.dat <- fishy.dat[fishy.dat$subject!="nl_NHK008",]
# dyslexia
fishy.dat <- fishy.dat[fishy.dat$subject!="nl_NHK022",]
# only completed Fishy and unreliable responses, no attention
fishy.dat <- fishy.dat[fishy.dat$subject!="nl_NHK043",]
# autism 
fishy.dat <- fishy.dat[fishy.dat$subject!="nl_NHK050",]


# Rename fishy.dat$dir_voice 
fishy.dat$dir_voice <- ifelse(fishy.dat$dir_voice=="male-gpr","F0","VTL")
fishy.dat$dir_voice<-as.factor(fishy.dat$dir_voice)

# Log-transformed thresholds
fishy.dat$thrs.a.log<-log(fishy.dat$threshold)
fishy.dat$thrs.g.log<-log(fishy.dat$threshold_geom)


c.cor<-merge.data.frame(c, fishy.dat, by='subject')

# Only child data
c.cor.kids<-c.cor[c.cor$group!="Adults",]
c.cor.kids$group<-droplevels(c.cor.kids$group)

# Create data subsets with only F0 or only VTL data
c.cor.kids.f0<-c.cor.kids[c.cor.kids$dir_voice=="F0",]
c.cor.kids.vtl<-c.cor.kids[c.cor.kids$dir_voice=="VTL",]


```


# RQ5 - Check correlation JNDs and weighting F0 and VTL Geometric mean
``` {r glmer correlation geom}
### For geometric mean

# For geometric mean
# look at correlation non-residuals
cor.test(x=c.cor.kids.f0$thrs.g.log, 
         y=c.cor.kids.f0$df0_bk, method="pearson")
cor.test(x=c.cor.kids.vtl$thrs.g.log, 
         y=c.cor.kids.vtl$dvtl_bk, method="pearson")

# subset of CI children
c.cor.kids.f0.ci<-c.cor.kids.f0[c.cor.kids.f0$CI=="CI",]
c.cor.kids.vtl.ci<-c.cor.kids.vtl[c.cor.kids.vtl$CI=="CI",]

cor.test(x=c.cor.kids.f0.ci$thrs.g.log, 
         y=c.cor.kids.f0.ci$df0_bk, method="pearson")
cor.test(x=c.cor.kids.vtl.ci$thrs.g.log, 
         y=c.cor.kids.vtl.ci$dvtl_bk, method="pearson")


# LM models with geometric mean
# lm model for F0 JNDs 
f0_m1_geom <- lm(thrs.g.log ~ age, data=c.cor.kids.f0.ci)

# lm model for VTL JNDs
vtl_m1_geom <- lm(thrs.g.log ~ age, data=c.cor.kids.vtl.ci)


# Assign residuals of F0 and VTL models to variables
r.f0.jnd<-residuals(f0_m1_geom)
r.vtl.jnd<-residuals(vtl_m1_geom)


# Merge residuals variables with data frames for F0 and VTL JNDs
c.cor.kids.f0.ci<-merge.data.frame(r.f0.jnd,c.cor.kids.f0.ci, by="row.names",all.x=TRUE)
c.cor.kids.f0.ci$r.f0.jnd <- c.cor.kids.f0.ci$x

c.cor.kids.vtl.ci<-merge.data.frame(r.vtl.jnd,c.cor.kids.vtl.ci, by="row.names",all.x=TRUE)
c.cor.kids.vtl.ci$r.vtl.jnd <- c.cor.kids.vtl.ci$x

# Set x to 0 for next merge of data frames
c.cor.kids.f0.ci$x<-NULL
c.cor.kids.vtl.ci$x<-NULL

# lm model for F0 cue weights
f0_m2 <- lm(df0_bk ~ age, data=c.cor.kids.f0.ci)
anova(f0_m2)
# lm model for VTL cue weights
vtl_m2 <- lm(dvtl_bk ~ age, data=c.cor.kids.vtl.ci)
anova(vtl_m2)

# Assign residual values of models to variables
r.f0.gen<-residuals(f0_m2)
r.vtl.gen<-residuals(vtl_m2)

# Merge residuals variables with data frames for F0 and VTL cue weights
c.cor.kids.f0.ci$r.f0.gen<-r.f0.gen
c.cor.kids.vtl.ci$r.vtl.gen <- r.vtl.gen


# Set x to 0 for next merge of data frames
c.cor.kids.f0.ci$x<-NULL
c.cor.kids.vtl.ci$x<-NULL


options(digits=7)


# Look at the correlation between residuals for F0 JNDs and residuals (fishy) for F0 coeffients (gender)
cor.test(c.cor.kids.f0.ci$r.f0.jnd,c.cor.kids.f0.ci$r.f0.gen)

# Look at the correlation between residuals for VTL JNDs and residuals (fishy) for VTL coeffients (gender)
cor.test(c.cor.kids.vtl.ci$r.vtl.jnd,c.cor.kids.vtl.ci$r.vtl.gen)




```




# Plot correlations
``` {r plots}


# e.g., setwd('C:/Users/leann/PICKA Experiments/')
setwd('C:/Users/leann/Desktop/CI Paper/Figures')

# # Add plot age variable for plot
# c.f0$plot_age<-c.f0$age
# c.f0[c.f0$group=="Adults",]$plot_age <- c(14.1, 14.3, 14.5, 14.6, 14.7, 14.8, 14.9, 15, 15.1, 15.2, 15.3, 15.4, 15.5, 15.7, 15.9)
# 
# c.vtl$plot_age<-c.vtl$age
# c.vtl[c.vtl$group=="Adults",]$plot_age <- c(14.1, 14.3, 14.5, 14.6, 14.7, 14.8, 14.9, 15, 15.1, 15.2, 15.3, 15.4, 15.5, 15.7, 15.9)
 

c.cor.kids.f0.ci$r.vtl.jnd<-0
c.cor.kids.f0.ci$r.vtl.gen<-0
c.cor.kids.vtl.ci$r.f0.jnd<-0
c.cor.kids.vtl.ci$r.f0.gen<-0

c.cor.kids.vtl.ci$Row.names<-NULL
c.cor.kids.f0.ci$Row.names<-NULL

c.g<-rbind(c.cor.kids.f0.ci, c.cor.kids.vtl.ci)

c.g$r.jnd<-0
c.g[c.g$dir_voice=="F0",]$r.jnd<-
  c.g[c.g$dir_voice=="F0",]$r.f0.jnd
c.g[c.g$dir_voice=="VTL",]$r.jnd<-
  c.g[c.g$dir_voice=="VTL",]$r.vtl.jnd

c.g$r.gen<-0
c.g[c.g$dir_voice=="F0",]$r.gen<-
  c.g[c.g$dir_voice=="F0",]$r.f0.gen
c.g[c.g$dir_voice=="VTL",]$r.gen<-
  c.g[c.g$dir_voice=="VTL",]$r.vtl.gen



# Plot E: correlation coefficients
# add regression line and confidence interval
e <- ggplot(c.g, aes(x = r.jnd, y = r.gen, color = group,
                     fill=group, group = 1, legend=TRUE)) +
  geom_point(size = 3,
         alpha=1,
         shape=21,
         color="black",
         show.legend=NA) +
  geom_smooth(aes(x = r.jnd, y = r.gen),method="lm", se=TRUE, fullrange=T,size=1) +
  scale_x_continuous(name = "Residuals JNDs") +
  scale_y_continuous(name = "Residuals cue weights") +
  scale_fill_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs")) +
    scale_color_manual(name = "Age groups", values = c("#00AFBB", "#E7B800", "#FC4E07","#F08700","#9E0059","#cef5c6"), labels = c("4-6 yrs","6-8 yrs","8-10 yrs","10-12 yrs","12-14 yrs","14-17 yrs")) +
  ggtitle("Correlation JNDs and Cue weights") +
  facet_wrap(~dir_voice) + 
  theme_bw() +
  # theme(plot.title = element_text(size = 18, face = "bold",hjust=0.5,
  #                                 margin = margin(t = 10,b = 20)),
  #       text = element_text(size = 16),
  #       axis.title = element_text(face="bold"),
  #       axis.text.x=element_text(size = 16, margin = margin(t = 10,b = 10)),
  #       axis.text.y=element_text(size = 16, margin = margin(l = 10,r = 10)))
    theme(plot.title = element_text(size = 18, face = "bold",hjust=0.5),
          legend.position = "bottom",
        text = element_text(size = 16),
        axis.text.x=element_text(size = 16, hjust=0.5),
        axis.text.y=element_text(size = 16, hjust=0.5),
        axis.title = element_text(face="bold"))

# Show plot E
e



e2 <-e +
  theme(plot.title = element_blank(),
        legend.text = element_text(size=12),
        text = element_text(size = 12),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 12, margin = margin(t = 1,b = 1)),
        axis.text.y=element_text(size = 12, margin = margin(l = 1,r = 1)))


ggsave(file="Figure 6 - Correlation Fishy x Gender.png", units = c("cm"), width = 15, height = 10, dpi = 600)



```


